Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-07-09 manuscripts/reply/reply-main.tex
Working on revisions of reply ms.

This is not surprising given the rich statistical literature that shows that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
% By using such priors on divergence times, we are essentially telling the
% method to favor models with few divergence times even if they do not
% explain the data very well.
Note, this is a statistical issue, extrinsic to \msb, and does not question the
soundness of the numerical approximation machinery of \msb.

@@

\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce
spurious support for models of temporally clustered divergences.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is highly sensitive to priors.

In this paper, we discuss the potential theoretical and practical
considerations of using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Here, we avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid spurious support of models with less parameter space.
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citep{Oaks2014dpp}.

\section{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their prior to reflect the large amount of uncertainty about the
timing of divergences across all 22 of the taxa in their study (see section
``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, resulting in too much
density in improbable regions of parameter space.

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid spurious support
of models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences under the empirically informed priors.

The main argument of \citet{Hickerson2013} is that the priors used by
\citet{Oaks2012} were not informative enough.
They suggest a very narrow, highly informed uniform prior on divergence times
is necessary to avoid the method's preference for models with few
divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

@@

Thus, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well-studied branch of Bayesian statistics that has given
rise to many inference methods that provide means of parameter estimation that
often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

\begin{linenomath}
Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the relative probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probability of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data (i.e., the maximum likelihood) and
the data are strongly informative relative to the prior, the values of the
parameters that maximize the posterior distribution will be relatively robust
to prior choice, even if the posterior distribution is technically incorrect
due to using the data to inform the priors.
This is why empirical Bayes can work well for estimating the values of model
parameters.
\end{linenomath}

@@

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model that
updates the prior to yield the model's posterior probability.
Thus the integral over the entire parameter space of the likelihood weighted by
the prior probability density is no longer a normalizing constant, but rather
is what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than parameter estimation.

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.
Also, unlike model parameters, the posterior probabilities of candidate
models have no clear true values.
% In some simple situations we might suspect that one model is correct and the
% rest are wrong, but in most applications, we know that all the models under
% consideration are oversimplifications of reality.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.
Nonetheless, empirical Bayesian model choice does perform well for some
problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems simultaneously, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.
However, this is far removed from the single model-choice problem of \msb.
In the Supporting Information we use a simple example to help highlight the
distinctions between Bayesian parameter estimation and model choice.

\subsection{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).

The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, will estimate model-averaged posteriors dominated by models that
exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow, and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's support of models with less parameter space.
Rather, the method strongly prefers the prior model with the narrowest
distribution on divergence times across all three of our analyses, even when
this model is almost certainly incorrect and excludes the true divergence times
of the Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

@@

Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude true divergence
times, making their results difficult to interpret.

@@

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22-population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the analysis described above using $1\e6$ random samples from
prior models $M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, retaining 1000 posterior
samples for each of the 1000 simulated datasets.

For each simulation replicate, we estimated the Bayes factor in favor
of excluding the truth as the ratio of the posterior to prior odds of
excluding the true value of at least one parameter.
Whenever the Bayes factor preferred a model excluding the truth we counted the
number of the 22 true divergence times that were excluded by the preferred
model.
Our results show that the model-averaging approach of \citet{Hickerson2013}
favors a model that excludes the true values of parameters in 97\% of the
replicates (90\% with GLM-regression adjustment), excluding up to 21 of the 22
true divergence times (Figure~\ref{figExclusionSimTau}).
We also used the mode estimate of the preferred model for each replicate to
estimate the number of true parameter values excluded, which produced very
similar results.
Importantly, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
Using a Bayes factor of greater than 10 as a criterion for strong support, 66\%
of the replicates (87\% with GLM-regression adjustment) strongly support the
exclusion of true values (Figure~\ref{figExclusionSimProb}).

@@

\subsection{Additional thoughts on empirical priors in Bayesian model choice}
The preceding sections are not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, when averaging over models with narrow and broad uniform priors on a
parameter with a likelihood density that is not expected to be uniformly
distributed, the posterior can be dominated by models that exclude from
consideration the true values of parameters due to the larger marginal
likelihoods of the models that are integrated over less space with high prior
weight yet low likelihood.

Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice, it is clear why one should use caution before overly
criticizing an investigator's choice of priors \emph{after} having seen the
resulting posterior.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty, as shown above, is to risk excluding the true values
one seeks to estimate.
However, continuous distributions more appropriate as priors for positive
real-valued parameters have been shown to greatly reduce spurious support for
clustered divergence models while allowing prior uncertainty to be accommodated
\citep{Oaks2014dpp}.

@@

Furthermore, our results demonstrate that the approach of \citet{Hickerson2013}
consistently infers highly clustered divergences across all the \divt{max} we
simulated (Figure~\ref{figPower4}A--D \& S\ref{figPower6}A--F).
The method is most likely to infer the extreme case of a single divergence
event shared across 22 taxa when populations diverged randomly over the past
\globalcoalunit generations.
When divergences are random over the past $8\globalpopsize$ generations, the
most likely inference is only two divergence events, and a single
divergence is still estimated in more than 10\% of the replicates.
It is interesting to note that as \divt{max} increases, but before the
estimates are finally pulled away from $\numt{} = 1$, the distribution of
\numt{} estimates closely mirror the U-shaped prior on divergence models
used by \msb (see Figure~\ref{figPower4}E and Oaks et al.'s
(\citeyear{Oaks2012}) Figure 5B).
This suggests this U-shaped prior coupled with the small marginal likelihoods
of models with many divergence parameters, is a major cause of the method's
bias toward clustered divergence models; this is consistent with
\citet{Oaks2012} and confirmed by \citet{Oaks2014dpp}.

@@

Our results show that the empirical Bayesian model-averaging approach leads to
spuriously strong support for the extreme case of a single divergence event
when populations diverged randomly over the last $8\globalpopsize$ generations.
To put this on the scale roughly consistent with a vertebrate mitochondrial
locus, assuming a mutation rate of $2\e{-8}$ per site per generation, this
translates to 5 million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.
Given the empirically Bayesian model-averaging approach of \citet{Hickerson2013}
lacks power to detect random variation in divergence times over such
timescales, it is difficult to justify the risk of the approach to exclude
regions of parameter space containing the truth.

>>>>

This is not surprising given the rich statistical literature that shows that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
\change{
% By using such priors on divergence times, we are essentially telling the
% method to favor models with few divergence times even if they do not
% explain the data very well.
This affect of the priors on marginal likelihoods creates a penalty for
over-parameterization in Bayesian model choice.
However, for this inference problem, the uniform priors on divergence times can
create a strong preference for simple models that are often of interest to
biogeographers even if these models do not explain the data very well.
This phenomenon is extrinsic to the numerical approximation machinery of \msb;
with such prior assumptions, the true posterior will favor models with
few divergence events.
However, such results, even if correct from the perspective of Bayesian model
choice, do not provide the biogeographical insights that a researcher who
employs \msb seeks to gain.
For example, a biogeographer would like to interpret the posterior probability
of a simultaneous divergence model as an estimate of the probability that this
model is correct.
However, when such prior assumptions are made about divergence times, the
estimated posterior probability is better interpretted as the probability that
you cannot completely rule out that the simultaneous-divergence model can
explain the data.
% Note, this is a statistical issue, extrinsic to \msb, and does not question the
% soundness of the numerical approximation machinery of \msb.
}

@@

\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times could increase the marginal likelihoods of models with more
divergence-time parameters and thus reduce spurious support for models of
temporally clustered divergences.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is highly sensitive to priors.

\change{
In this paper, we discuss theoretical and practical considerations of using
empirically informed priors for Bayesian model choice.
}
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Here, we avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citep{Oaks2014dpp}.

\section{The potential implications of empirical Bayesian model choice}
\change{
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences when using a prior on divergence times that is strongly
informed by the data being analyzed.
The main argument of \citet{Hickerson2013} is that the priors used by
\citet{Oaks2012} were not informative enough.
}
%
% \citet{Hickerson2013} repeatedly refer to the prior distributions used by
% \citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
% However, this is misleading, as \citet{Oaks2012} discuss in detail how they
% selected their prior to reflect the large amount of uncertainty about the
% timing of divergences across all 22 of the taxa in their study (see section
% ``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
% \citet{Oaks2012} further discuss how the use of uniform prior distributions in
% \msb for many of the model's parameters requires investigators to select broad
% priors to avoid excluding the truth \textit{a priori}, resulting in too much
% density in improbable regions of parameter space.

% \citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
% data to inform their prior on divergence times (i.e., an empirical Bayesian
% approach).
% However, \citet{Oaks2012} did use empirically informed priors to mimic
% empirical situations in which a large amount of prior information is available;
% they did so to assess the prior sensitivity of the method and to determine if
% uniform priors in such situations are narrow enough to avoid spurious support
% of models with few divergence-time parameters.
% The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
% highly sensitive to the prior on divergence times.
% Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
% divergences under the empirically informed priors.
%
% The main argument of \citet{Hickerson2013} is that the priors used by
% \citet{Oaks2012} were not informative enough.
They suggest a very narrow, highly informed uniform prior on divergence times
is necessary to avoid the method's preference for models with few
divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

@@

Thus, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well-studied branch of Bayesian statistics that has given
rise to many inference methods that provide means of parameter estimation that
often exhibit favorable frequentist properties.
% Furthermore, many post-hoc correction methods have been developed for
% estimating confidence-intervals from empirical Bayes estimates of
% distributions that often exhibit well-behaved frequentist coverage
% probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

\begin{linenomath}
Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the relative probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probability of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data (i.e., the maximum likelihood) and
the data are strongly informative relative to the prior, the values of the
parameters that maximize the posterior distribution will be relatively robust
to prior choice, even if the posterior distribution is technically incorrect
due to using the data to inform the priors.
By giving the data more weight relative to the prior, the goal is that the
posterior distribution will be peaked near the true value(s) of the model's
parameter(s).
% This is why empirical Bayes can work well for estimating the values of model
% parameters.
\end{linenomath}

@@

However, if we look at Equation~\ref{eq:bayesmodelchoice}, we see that in
Bayesian model choice it is now the \emph{marginal} likelihood of a model that
updates the prior to yield the model's posterior probability.
Thus the integral over the entire parameter space of the likelihood weighted by
the prior probability density is no longer a normalizing constant, but rather
is what informs the posterior probability of that model from the data.
As a result, Bayesian model choice tends to be much more sensitive to priors
than parameter estimation.
Also, unlike model parameters, the posterior probabilities of candidate
models have no clear true values.
% There is no such justification for empirical Bayesian model choice, because
% there are no true values for the model probabilities being estimated.
Model posterior probabilities are inherently measures of our belief in the
models after our prior beliefs are updated by the data being analyzed.
This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.

Another important difference of Bayesian model choice illustrated by
Equation~\ref{eq:bayesmodelchoice} is that the value of interest, the
posterior probability of a model, is not a function of \myTheta{}, because
it is integrated out of the marginal likelihoods of the candidate models.
Thus, unlike parameter estimates, the estimated posterior probability of a
model is a single value (rather than a distribution) lacking a measure of
posterior uncertainty.
% In some simple situations we might suspect that one model is correct and the
% rest are wrong, but in most applications, we know that all the models under
% consideration are oversimplifications of reality.

Nonetheless, empirical Bayesian model choice does perform well for some
problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems simultaneously, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.
However, this is far removed from the single model-choice problem of \msb.
In the Supporting Information we use a simple example to help highlight the
distinctions between Bayesian parameter estimation and model choice.

\subsection{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors.
% for a method that has already been shown to be biased toward models with less
% parameter space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa.
%, a major problem when using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).

\change{
Hickerson et al.'s \citeyear{Hickerson2013} results that strongly prefer the
narrowest priors on divergence times (their $M_1$ and $M_2$) suggest their
approach is biased toward models with less parameter space, and as a
consequence, will estimate model-averaged posteriors dominated by models that
exclude true values of model's parameters.
}
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow, and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's support of models with less parameter space.
Rather, the method strongly prefers the prior model with the narrowest
distribution on divergence times across all three of our analyses, even when
this model is incorrect and excludes the true divergence times
of the Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

@@

% Given that the results of \citet{Hickerson2013} strongly prefer the models with
% the narrowest prior on divergence times, it seems quite likely that their
% model-averaged results are dominated by models that exclude true divergence
% times, making their results difficult to interpret.

@@

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22-population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the analysis described above using $1\e6$ random samples from
each of the prior models $M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, retaining 1000
posterior samples for each of the 1000 simulated datasets.

For each simulation replicate, we estimated the Bayes factor in favor
of excluding the truth as the ratio of the posterior to prior odds of
excluding the true value of at least one parameter.
Whenever the Bayes factor preferred a model excluding the truth we counted the
number of the 22 true divergence times that were excluded by the preferred
model.
Our results show that the model-averaging approach of \citet{Hickerson2013}
favors a model that excludes the true values of parameters in 97\% of the
replicates (90\% with GLM-regression adjustment), excluding up to 21 of the 22
true divergence times (Figure~\ref{figExclusionSimTau}).
We also used the mode estimate of the preferred model for each replicate to
estimate the number of true parameter values excluded, which produced nearly
identical results.
Importantly, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
Using a Bayes factor of greater than 10 as a criterion for strong support, 66\%
of the replicates (87\% with GLM-regression adjustment) strongly support the
exclusion of true values (Figure~\ref{figExclusionSimProb}).

@@

\subsection{Additional thoughts on empirical priors in Bayesian model choice}
The preceding sections are not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, when averaging over models with narrow and broad uniform priors on a
parameter with a likelihood density that is not expected to be uniformly
distributed, the posterior can be dominated by models that exclude from
consideration the true values of parameters due to the larger marginal
likelihoods of the models that are integrated over less space with high prior
weight yet low likelihood.
\change{
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty is to risk excluding the true values one seeks to
estimate, as shown above.
However, continuous distributions more appropriate as priors for positive
real-valued parameters have been shown to greatly reduce spurious support for
clustered divergence models while allowing prior uncertainty to be accommodated
\citep{Oaks2014dpp}.
}

% Given the theoretical and practical issues with empirical Bayes approaches to
% Bayesian model choice, it is clear why one should use caution before overly
% criticizing an investigator's choice of priors \emph{after} having seen the
% resulting posterior.
% As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
% large amount of uncertainty regarding the divergence times of the 22 population
% pairs under study.
% Two of these pairs represent distinct species, and the taxonomy of many groups
% in the Philippines has repeatedly been shown to mask deeply divergent lineages
% \citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
% Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.

@@

Furthermore, our results demonstrate that the approach of \citet{Hickerson2013}
consistently infers highly clustered divergences across all the \divt{max} we
simulated (Figure~\ref{figPower4}A--D \& S\ref{figPower6}A--F).
The method is most likely to infer the extreme case of a single divergence
event shared across all 22 taxa when populations diverged randomly over the
past \globalcoalunit generations.
When divergences are random over the past $8\globalpopsize$ generations, the
most likely inference is only two divergence events, and a single
divergence is still estimated in more than 10\% of the replicates.
It is interesting to note that as \divt{max} increases, but before the
estimates are finally pulled away from $\numt{} = 1$, the distribution of
\numt{} estimates closely mirror the U-shaped prior on divergence models
used by \msb (see Figure~\ref{figPower4}E and Oaks et al.'s
(\citeyear{Oaks2012}) Figure 5B).
This suggests this U-shaped prior coupled with the small marginal likelihoods
of models with many divergence parameters, is a major cause of the method's
bias toward clustered divergence models; this is consistent with
\citet{Oaks2012} and confirmed by \citet{Oaks2014dpp}.

@@

Our results show that the empirical Bayesian model-averaging approach leads to
spuriously strong support for the extreme case of a single divergence event
when populations diverged randomly over the last $8\globalpopsize$ generations.
To put this on the scale roughly consistent with a vertebrate mitochondrial
locus, assuming a mutation rate of $2\e{-8}$ per site per generation, this
translates to 5 million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.
% Given the empirically Bayesian model-averaging approach of \citet{Hickerson2013}
% lacks power to detect random variation in divergence times over such
% timescales, it is difficult to justify the risk of the approach to exclude
% regions of parameter space containing the truth.

Also, the results of our power analyses further demonstrate the propensity of
Hickerson et al.'s (\citeyear{Hickerson2013}) approach to exclude true
parameter values.
Across all but one of the \divt{max} we simulated, in a large proportion of
replicates the method favors a model that excludes the truth, and across many
of the \divt{max} the preferred model will exclude a large proportion of the
true divergence-time values (Figure~\ref{figPowerExclusion4}A--D \&
S\ref{figPowerExclusion6}A--F).
Importantly, the posterior probability of excluding at least one true
divergence value is also quite high across many of the \divt{max}
(Figure~\ref{figPowerExclusion4}E--H \& S\ref{figPowerExclusion6}G--L).
Only when the data are identically distributed as one of the prior models does
the method avoid excluding the truth more than 5\% of the time
(Figure~\ref{figPowerExclusion4}C).
% Again, this demonstrates the method's sensitivity to priors.
